### 2017-06-27 Plos-one-manuscript/latex/manuscript.tex
working on review

\section*{Introduction}
The open source development model, initially applied to software, is thriving in the development of open source scientific equipment due in part to increasing access of 3D printing\cite{Baden2015,Pearce2013}.
Additive manufacturing methods have existed for decades although the recent availability of inexpensive desktop printers\cite{MakerbotIndustries,RepRap} have made it feasible for consumers to design and print prototypes and even functional parts, and consumer goods\cite{Fullerton2014,Wittbrodt2013}.
Proliferation of free CAD software\cite{OpenScad,Blender,SketchUp,123D} and design sharing sites\cite{Thingiverse,NationalInstitutesofHealth,GrabCAD,GitHubInc} have also supported the growth and popularity of open designed parts and projects.
Open design 3D-printable lab equipment is an attractive idea because, like open source software, it allows free access to technology that is otherwise inaccessible due to proprietary and/or financial barriers. 
Open design tools create opportunity for scientists and educational programs in remote or resource limited areas to participate with inexpensive and easy to make tools\cite{Marzullo2012,Lang2011,Fobel2013,Baker2014,Cybulski2014}.
Open source development also enables the development of custom solutions to meet unique applications not met by commercial products that are shared freely and are user modifiable\cite{Fullerton2014,Pearce2012,Rankin2014,Sulkin2013,Dryden2015,DaCosta2014,Tek2008}.
Some advanced, noteworthy, open source scientific equipment include a PCR device\cite{ChaiBiotechnologiesInc2015}, and a two-photon microscope\cite{Rosenegger2014} although simple tools have potential to be impactful as they can serve a wider community.

Some simple and clever printable parts that have emerged are ones that give a new function to a ubiquitous existing device, such as drill bit attachment designed to hold centrifuge tubes, allowing a dremel to be used as a centrifuge\cite{Garvey2009}.
Although this may make a rather crude centrifuge it may be an adequate solution for a fraction of the cost of a commercial centrifuge.
Other examples of open source research tools that utilize 3D printed parts include optics equipment\cite{Zhang2013}, microscopes\cite{Baden2014a,Walus2014}, syringe pumps\cite{Wijnen2014}, reactionware\cite{Symes2012,Kitson2012,Mathieson2013,Kitson2014}, microfluidics\cite{Brennan2015,Dragone2013} and the list continues to grow\cite{PlosCollections}.

One example of a everyday scientific tool that provides opportunity for an open design solution is the micropipette.
An open design micropipette that can be made cheaply affords more options for labs and educational settings.
Micropipettes are an indispensable tool used routinely in lab tasks and can easily cost \$1000 USD for a set.
Often a lab will require several sets each for a dedicated task.
Some pipettes may even re-calibrated for use with liquids of different properties.

Air displacement pipettes use a piston operating principal to draw liquid into the pipette\cite{ISO8655}.
In a typical commercial pipette the piston is made to be gas-tight with a gasketed plunger inside a smooth barrel.
Consumer grade fused deposition modeling (FDM) printers are unable to build a smooth surface do to the formation of ridges that occur as each layer is deposited.
The ridges formed by FDM make it impractical to form a gas-tight seal between moving parts, even with a gasket.
Existing printable open-design micropipettes get around this limitation by stretching a membrane over one end of a printed tube, which when pressed causes the displacement.
The displacement membrane can be made from any elastic material such as a latex glove.
A few open design micropipettes exist including a popular one which, in addition to the printed parts, uses parts scavenged from a retractable pen\cite{Baden2014}.
Because there is no built in feature such as a readout for the user to set the displacement to a desired volume, this design requires the user to validate the volumes dispensed with a high precision scale.
Without verification with a scale the volumes dispensed can only be estimated based on calculations of the deflection of the membrane which is not a practical protocol.

@@

\begin{figure}
	\caption{
		{\bf CAD renderings of assembled pipette and function.} The pipette actuates the syringe to three positions. {\bf (A) The latched position.} When the plunger is pressed the pipette locks at this position. The tip is then placed in a liquid and the unlatching button is pressed to release the pipette back to the set position (B), drawing in liquid.  {\bf(B) The set position.} The position of the screw determines the total displacement that the plunger moves. The pipette is spring loaded to return to this position. {\bf (C) The blow-out position.} The fluid is transferred by pressing the plunger past the latched position to blow-out all the liquid. {\bf (D) Return to the latched position.} The pipette returns to the latched position ready to preform another transfer.
	}
	\label{fig2}
\end{figure}

@@

\section*{Results and Discussion}
Validation testing preformed with the existing graduations printed on the syringes did not meet the ISO standards.
According to ISO 8655 for a pipette with the maximum nominal volume of 1000 $\mu$L the systematic error cannot exceed 8 $\mu$L and the random error cannot exceed 3 $\mu$L.
For the maximum nominal volume of 300 $\mu$L the systemic error cannot exceed 4 $\mu$L and the random error cannot exceed 1.5 $\mu$L.
The commercial pipettes met these standards handily, but in our initial tests with our printed pipette we noticed large negative systematic error suggesting that we were missing a biasing factor. 
This error was exaggerated while transferring larger volumes.
After further investigation we realized that the graduations are intended to measure incompressible fluids within the syringe while we were using them to measure air while under vacuum.
Because the syringe graduations were used to measure the air under vacuum it could not be expected to serve as a 1:1 volume ratio of water that was pulled into the tip because under vacuum the air had expanded.
This explains the negative systematic error we were experiencing.
The water in the tip pulls on the air due to gravity which causes it to expand slightly but enough to make measuring with the graduation in this way inaccurate.
Our solution was to replace the built-in scale with a scale that accounted for the expansion.
Using the data from our initial testing we calculated a factor for the expansion and used that to make the new scale (\nameref{S1_Fig} and \nameref{S1_Fig}.)
With the new scale taped on the syringe our validation testing met the ISO 8655 standard.
Replacing the scale with our scale that accounts for the expansion corrected this effect. 
Our printed pipette with the adjusted scale meets ISO standards for accuracy and precision. (Table \ref{table3} and \ref{table4}).

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
\begin{table}[!ht]
	\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
		\centering
		\caption{ISO 8655 for 100-1000 $\mu$L comparing a commercial pipette with our printed pipette used with existing 3 mL syringe scale and an adjusted scale}
		\label{table3}
		\begin{tabular}{lllllll}
			&                       & Mean   & Systematic Error & \% Sys. err. & Random Error & \% Rand. err. \\
			1000 $\mu$L & ISO 8655, 100-1000 $\mu$L & 1000    & 8.00             & 0.80         & 3.00         & 0.30          \\
			& Commercial Pipette    & 1002.98 & 2.98             & 0.30         & 1.72         & 0.17          \\
			& Printed Pipette       & 949.29  & -50.71           & -5.07        & 0.60         & 0.06          \\
			& Printed Pipette Scale & 1003.57 & 3.57             & 0.36         & 0.89         & 0.09          \\
			&                       &         &                  &              &              &               \\
			500 $\mu$L  & ISO 8655, 100-1000 $\mu$L & 500     & 8.00             & 1.60         & 3.00         & 0.60          \\
			& Commercial Pipette    & 503.67  & 3.67             & 0.73         & 0.49         & 0.10          \\
			& Printed Pipette       & 475.99  & -24.01           & -4.80        & 4.75         & 1.00          \\
			& Printed Pipette Scale & 503.62  & 3.62             & 0.72         & 1.64         & 0.33          \\
			&                       &         &                  &              &              &               \\
			200 $\mu$L  & ISO 8655, 100-1000 $\mu$L & 200     & 8.00             & 4.00         & 3.00         & 1.50          \\
			& Commercial Pipette    & 204.61  & 4.61             & 2.30         & 0.15         & 0.07          \\
			& Printed Pipette       & 186.55  & -13.45           & -6.72        & 1.31         & 0.70          \\
			& Printed Pipette Scale & 201.87  & 1.87             & 0.94         & 1.47         & 0.73          \\
			&                       &         &                  &              &              &               \\
			100 $\mu$L  & ISO 8655, 100-1000 $\mu$L & 100     & 8.00             & 8.00         & 3.00         & 3.00          \\
			& Commercial Pipette    & 104.29  & 4.29             & 4.29         & 1.65         & 1.58          \\
			& Printed Pipette       & 94.02   & -5.98            & -5.98        & 4.81         & 5.12          \\
			& Printed Pipette Scale & 101.00  & 1.00             & 1.00         & 1.05         & 1.04         
		\end{tabular}
		%\begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl. Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
		%\end{flushleft}
	\end{adjustwidth}
\end{table}

\begin{table}[!ht]
	\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
		\centering
		\caption{ISO 8655 for 30-300 $\mu$L comparing a commercial pipette with our printed pipette used with existing 3 mL syringe scale and an adjusted scale}
		\label{table4}
		\begin{tabular}{lllllll}
			&                       & Mean   & Systematic Error & \% Sys. err. & Random Error & \% Rand. err. \\
			300 $\mu$L & ISO 8655, 30-300 $\mu$L   & 300    & 4.00             & 1.33         & 1.50         & 0.50          \\
			& Commercial Pipette    & 301.19 & 1.19             & 0.40         & 0.53         & 0.18          \\
			& Printed Pipette       & 286.91 & -13.09           & -4.36        & 0.42         & 0.15          \\
			& Printed Pipette Scale & 299.11 & -0.89            & -0.30        & 0.48         & 0.16          \\
			&                       &        &                  &              &              &               \\
			200 $\mu$L & ISO 8655, 30-300 $\mu$L   & 200    & 4                & 2            & 1.5          & 0.75          \\
			& Commercial Pipette    & 200.06 & 0.06             & 0.03         & 0.46         & 0.23          \\
			& Printed Pipette       & 193.40 & -6.60            & -3.30        & 2.86         & 1.48          \\
			& Printed Pipette Scale & 200.57 & 0.57             & 0.28         & 0.86         & 0.43          \\
			&                       &        &                  &              &              &               \\
			50 $\mu$L  & ISO 8655, 30-300 $\mu$L   & 50     & 4                & 8            & 1.5          & 3             \\
			& Commercial Pipette    & 49.02  & -0.98            & -1.96        & 0.10         & 0.20          \\
			& Printed Pipette       & 49.62  & -0.38            & -0.76        & 1.26         & 2.53          \\
			& Printed Pipette Scale & 48.73  & -1.27            & -2.54        & 1.11         & 2.27          \\
			&                       &        &                  &              &              &               \\
			30 $\mu$L  & ISO 8655, 30-300 $\mu$L   & 30     & 4                & 13.3         & 1.5          & 5             \\
			& Commercial Pipette    & 29.08  & -0.92            & -3.06        & 0.09         & 0.31          \\
			& Printed Pipette       & 29.22  & -0.78            & -2.59        & 0.31         & 1.07          \\
			& Printed Pipette Scale & 27.78  & -2.22            & -7.41        & 1.37         & 4.93          \\
			&                       &        &                  &              &              &               \\
			20 $\mu$L* & ISO 8655, 30-300 $\mu$L   & 20     & 4                & 20           & 1.5          & 7.5           \\
			& Commercial Pipette    & NA     & NA               & NA           & NA           & NA            \\
			& Printed Pipette       & 18.70  & -1.30            & -6.48        & 0.38         & 2.01          \\
			& Printed Pipette Scale & 17.94  & -2.06            & -10.29       & 1.87         & 10.42         \\
			&                       &        &                  &              &              &               \\
			10 $\mu$L* & ISO 8655, 30-300 $\mu$L   & 10     & 4                & 40           & 1.5          & 15            \\
			& Commercial Pipette    & NA     & NA               & NA           & NA           & NA            \\
			& Printed Pipette       & 11.95  & 1.95             & 19.52        & 0.73         & 6.08          \\
			& Printed Pipette Scale & 7.64   & -2.36            & -23.64       & 0.38         & 4.92         
		\end{tabular}
		\begin{flushleft} * The 20 $\mu$L and 10 $\mu$L volumes are out of the range in this case but we wanted to demonstrate that the pipette is capable of even smaller volumes.
		\end{flushleft}
	\end{adjustwidth}
\end{table}

@@

The open design nature of this project encourages anyone to use and submit changes to improve and add features to this design.
All of the working files and documentation are kept in a public repository~\cite{BMLmicropipette}.
Future directions for this project include developing a tip ejection system and additional configurations for transferring volumes below 30 uL as well as increasing over all user friendliness, such as making the adjusting bolt easier to grip and improving ergonomics.

@@

\subsection*{S1 Video}
\label{S1_Video}
{\bf Video showing assembly and demonstration of operation.} Assembly of the pipette in the 100-1000 $\mu$L and 30-300 $\mu$L configuration is preformed. https://www.youtube.com/watch?v=D8y5WUYpcW0

>>>>

\section*{Introduction}
The open source development model, initially applied to software, is thriving in the development of open source scientific equipment due in part to increasing access of 3D printing\cite{Baden2015,Pearce2013}.
Additive manufacturing methods have existed for decades although the recent availability of inexpensive desktop printers\cite{MakerbotIndustries,RepRap} have made it feasible for consumers to design and print prototypes and even functional parts, and consumer goods\cite{Fullerton2014,Wittbrodt2013}.
Proliferation of free CAD software\cite{OpenScad,Blender,SketchUp,123D} and design sharing sites\cite{Thingiverse,NationalInstitutesofHealth,GrabCAD,GitHubInc} have also supported the growth and popularity of open designed parts and projects.
Open design 3D-printable lab equipment is an attractive idea because, like open source software, it allows free access to technology that is otherwise inaccessible due to proprietary and/or financial barriers. 
Open design tools create opportunity for scientists and educational programs in remote or resource limited areas to participate with inexpensive and easy to make tools\cite{Marzullo2012,Lang2011,Fobel2013,Baker2014,Cybulski2014,Bhamla2017}.
Open source development also enables the development of custom solutions to meet unique applications not met by commercial products that are shared freely and are user modifiable\cite{Fullerton2014,Pearce2012,Rankin2014,Sulkin2013,Dryden2015,DaCosta2014,Tek2008}.
Some advanced, noteworthy, open source scientific equipment include a PCR device\cite{ChaiBiotechnologiesInc2015}, a tissue scaffold printer\cite{Trachtenberg2014}, and a two-photon microscope\cite{Rosenegger2014} although simple tools have potential to be impactful as they can serve a wider community.

Some simple and clever printable parts that have emerged are ones that give a new function to a ubiquitous existing device, such as drill bit attachment designed to hold centrifuge tubes, allowing a dremel to be used as a centrifuge\cite{Garvey2009}.
Although this may make a rather crude centrifuge it may be an adequate solution for a fraction of the cost of a commercial centrifuge.
Other examples of open source research tools that utilize 3D printed parts include optics equipment\cite{Zhang2013}, microscopes\cite{Baden2014a,Walus2014}, syringe pumps\cite{Wijnen2014,Patrick2015}, reactionware\cite{Symes2012,Kitson2012,Mathieson2013,Kitson2014}, microfluidics\cite{Brennan2015,Dragone2013} and the list continues to grow\cite{PlosCollections}.

One example of an everyday scientific tool that provides opportunity for an open design solution is the micropipette.
An open design micropipette that can be made cheaply affords more options for labs and educational settings.
Micropipettes are an indispensable tool used routinely in lab tasks and can easily cost \$1000 USD for a set.
Often a lab will require several sets each for a dedicated task.
Some pipettes may even be re-calibrated for use with liquids of different properties.

Air displacement pipettes use a piston operating principle to draw liquid into the pipette\cite{ISO8655}.
In a typical commercial pipette the piston is made to be gas-tight with a gasketed plunger inside a smooth barrel.
Consumer grade fused deposition modeling (FDM) printers are unable to build a smooth surface due to the formation of ridges that occur as each layer is deposited\cite{Takagishi2017}.
The ridges formed by FDM make it impractical to form a gas-tight seal between moving parts, even with a gasket.
Existing printable open-design micropipettes get around this limitation by stretching a membrane over one end of a printed tube, which when pressed causes the displacement.
The displacement membrane can be made from any elastic material such as a latex glove.
A few open design micropipettes exist including a popular one which, in addition to the printed parts, uses parts scavenged from a retractable pen\cite{Baden2014}.
Because there is no built in feature such as a readout for the user to set the displacement to a desired volume, this design requires the user to validate the volumes dispensed with a high precision scale.
Without verification with a scale the volumes dispensed can only be estimated based on calculations of the deflection of the membrane which is not a practical protocol.

@@

\begin{figure}
	\caption{
		{\bf CAD renderings of assembled pipette and function.} The pipette actuates the syringe to three positions. {\bf (A) The latched position.} When the plunger is pressed the pipette locks at this position. The tip is then placed in a liquid and the unlatching button is pressed to release the pipette back to the set position (B), drawing in liquid.  {\bf(B) The set position.} The position of the screw determines the total displacement that the plunger moves. The pipette is spring loaded to return to this position. {\bf (C) The blow-out position.} The fluid is transferred by pressing the plunger past the latched position to blow-out all the liquid. {\bf (D) Return to the latched position.} The pipette returns to the latched position ready to perform another transfer.
	}
	\label{fig2}
\end{figure}

@@

\section*{Results and Discussion}
Validation testing performed with the existing graduations printed on the syringes did not meet the ISO standards.
According to ISO 8655 for a pipette with the maximum nominal volume of 1000 $\mu$L the systematic error cannot exceed 8 $\mu$L and the random error cannot exceed 3 $\mu$L.
For the maximum nominal volume of 300 $\mu$L the systemic error cannot exceed 4 $\mu$L and the random error cannot exceed 1.5 $\mu$L.
The commercial pipettes met these standards handily, but in our initial tests with our printed pipette we noticed large negative systematic error suggesting that we were missing a biasing factor. 
This error was exaggerated while transferring larger volumes.
After further investigation we realized that the graduations are intended to measure incompressible fluids within the syringe while we were using them to measure air while under vacuum.
Because the syringe graduations were used to measure the air under vacuum it could not be expected to serve as a 1:1 volume ratio of water that was pulled into the tip because under vacuum the air had expanded.
This explains the negative systematic error we were experiencing.
The water in the tip pulls on the air due to gravity which causes it to expand slightly but enough to make measuring with the graduation in this way inaccurate.

Our solution was to replace the built-in scale with a scale that accounted for the expansion.
We compared expected volumes with actual measurements and noticed a linear relationship.
We scaled up the graduations by a factor of 1.027x for both the 100-1000 $\mu$L, and 30-300 $\mu$L configurations.
These scales were exported to portable document format (PDF) so that they are most easily printed to scale.
These adjusted scales are printed on a transparency sheet and taped onto the syringe with the zero at plunger in the latched position (\nameref{S1_Fig} and \nameref{S1_Fig}).

With the new scale taped on the syringe our validation testing met the ISO 8655 standard.
Replacing the scale with our scale that accounts for the expansion corrected this effect. 
Our printed pipette with the adjusted scale meets ISO standards for accuracy and precision. (Table \ref{table3} and \ref{table4}).

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
\begin{table}[!ht]
	\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
		\centering
		\caption{ISO 8655 for 100-1000 $\mu$L comparing a commercial pipette with our printed pipette used with existing 3 mL syringe scale and an adjusted scale}
		\label{table3}
		\begin{tabular}{llccccc}
			&                       & Mean   & Systematic Error & \% Sys. err. & Random Error & \% Rand. err. \\
			1000 $\mu$L & ISO 8655, 100-1000 $\mu$L & 1000    & 8.00             & 0.80         & 3.00         & 0.30          \\
			& Commercial Pipette    & 1002.98 & 2.98             & 0.30         & 1.72         & 0.17          \\
			& Printed Pipette       & 949.29  & -50.71           & -5.07        & 0.60         & 0.06          \\
			& Printed Pipette Scale & 1003.57 & 3.57             & 0.36         & 0.89         & 0.09          \\
			&                       &         &                  &              &              &               \\
			500 $\mu$L  & ISO 8655, 100-1000 $\mu$L & 500     & 8.00             & 1.60         & 3.00         & 0.60          \\
			& Commercial Pipette    & 503.67  & 3.67             & 0.73         & 0.49         & 0.10          \\
			& Printed Pipette       & 475.99  & -24.01           & -4.80        & 4.75         & 1.00          \\
			& Printed Pipette Scale & 503.62  & 3.62             & 0.72         & 1.64         & 0.33          \\
			&                       &         &                  &              &              &               \\
			200 $\mu$L  & ISO 8655, 100-1000 $\mu$L & 200     & 8.00             & 4.00         & 3.00         & 1.50          \\
			& Commercial Pipette    & 204.61  & 4.61             & 2.30         & 0.15         & 0.07          \\
			& Printed Pipette       & 186.55  & -13.45           & -6.72        & 1.31         & 0.70          \\
			& Printed Pipette Scale & 201.87  & 1.87             & 0.94         & 1.47         & 0.73          \\
			&                       &         &                  &              &              &               \\
			100 $\mu$L  & ISO 8655, 100-1000 $\mu$L & 100     & 8.00             & 8.00         & 3.00         & 3.00          \\
			& Commercial Pipette    & 104.29  & 4.29             & 4.29         & 1.65         & 1.58          \\
			& Printed Pipette       & 94.02   & -5.98            & -5.98        & 4.81         & 5.12          \\
			& Printed Pipette Scale & 101.00  & 1.00             & 1.00         & 1.05         & 1.04         
		\end{tabular}
		%\begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl. Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
		%\end{flushleft}
	\end{adjustwidth}
\end{table}

\begin{table}[!ht]
	\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
		\centering
		\caption{ISO 8655 for 30-300 $\mu$L comparing a commercial pipette with our printed pipette used with existing 3 mL syringe scale and an adjusted scale}
		\label{table4}
		\begin{tabular}{llccccc}
			&                       & Mean   & Systematic Error & \% Sys. err. & Random Error & \% Rand. err. \\
			300 $\mu$L & ISO 8655, 30-300 $\mu$L   & 300    & 4.00             & 1.33         & 1.50         & 0.50          \\
			& Commercial Pipette    & 301.19 & 1.19             & 0.40         & 0.53         & 0.18          \\
			& Printed Pipette       & 286.91 & -13.09           & -4.36        & 0.42         & 0.15          \\
			& Printed Pipette Scale & 299.11 & -0.89            & -0.30        & 0.48         & 0.16          \\
			&                       &        &                  &              &              &               \\
			200 $\mu$L & ISO 8655, 30-300 $\mu$L   & 200    & 4                & 2            & 1.5          & 0.75          \\
			& Commercial Pipette    & 200.06 & 0.06             & 0.03         & 0.46         & 0.23          \\
			& Printed Pipette       & 193.40 & -6.60            & -3.30        & 2.86         & 1.48          \\
			& Printed Pipette Scale & 200.57 & 0.57             & 0.28         & 0.86         & 0.43          \\
			&                       &        &                  &              &              &               \\
			50 $\mu$L  & ISO 8655, 30-300 $\mu$L   & 50     & 4                & 8            & 1.5          & 3             \\
			& Commercial Pipette    & 49.02  & -0.98            & -1.96        & 0.10         & 0.20          \\
			& Printed Pipette       & 49.62  & -0.38            & -0.76        & 1.26         & 2.53          \\
			& Printed Pipette Scale & 48.73  & -1.27            & -2.54        & 1.11         & 2.27          \\
			&                       &        &                  &              &              &               \\
			30 $\mu$L  & ISO 8655, 30-300 $\mu$L   & 30     & 4                & 13.3         & 1.5          & 5             \\
			& Commercial Pipette    & 29.08  & -0.92            & -3.06        & 0.09         & 0.31          \\
			& Printed Pipette       & 29.22  & -0.78            & -2.59        & 0.31         & 1.07          \\
			& Printed Pipette Scale & 27.78  & -2.22            & -7.41        & 1.37         & 4.93          \\
			&                       &        &                  &              &              &               \\         
		\end{tabular}
	\end{adjustwidth}
\end{table}

@@

The open design nature of this project encourages anyone to use and submit changes to improve and add features to this design.
All of the working files and documentation are kept in a public repository~\cite{BMLmicropipette}.
Future directions for this project include developing a tip ejection system and additional configurations for transferring volumes below 30 uL as well as increasing over all user friendliness, such as making the adjusting bolt easier to grip and improving ergonomics.
It's our hope that this project is under continuous development and compatibility with different syringes and printers can be crowd-sourced from community contributors.

@@

\subsection*{S1 Video}
\label{S1_Video}
{\bf Video showing assembly and demonstration of operation.} Assembly of the pipette in the 100-1000 $\mu$L and 30-300 $\mu$L configuration is performed. https://www.youtube.com/watch?v=D8y5WUYpcW0
